### 2015-08-28 books/Logic_of_Political_Survival_Mesquita/code/ch41.tex
-

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('bdm2s2_nation_year_data_may2002.csv')
df['Klepto'] = (df['TAXGDP']-df['Expenditure']).abs()
df = df[['regyr','ccode','aid_gdp','lrgdpc','pop','year','W','S','Klepto','laglrgdpc']]
\end{minted}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Growth and lagged change in W

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('../bdm2s2_nation_year_data_may2002.csv')
df = df.sort_index(by=['ccode','year'],ascending=True)
\end{minted}

If ccode at t-2 is different for current, than delta W for this instance
makes no sense, drop them.

\begin{minted}[fontsize=\footnotesize]{python}
df2 = df.copy()
df2['polchange'] = (df2.W-df2.shift(2).W)**2
df2['DW20'] = df2.W-df2.shift(2).W
df2['dummy'] = df2.ccode-df2.shift(2).ccode
df2 = df2[df2.dummy == 0]
print len(df2)
\end{minted}

\begin{verbatim}
19059
\end{verbatim}

\begin{minted}[fontsize=\footnotesize]{python}
import statsmodels.formula.api as smf
results = smf.ols('WB_growth ~ W + S + DW20 + polchange + np.log(pop)', data=df2).fit()
print results.summary()
\end{minted}

\begin{verbatim}
                            OLS Regression Results                            
==============================================================================
Dep. Variable:              WB_growth   R-squared:                       0.005
Model:                            OLS   Adj. R-squared:                  0.003
Method:                 Least Squares   F-statistic:                     3.315
Date:                Tue, 25 Aug 2015   Prob (F-statistic):            0.00545
Time:                        20:18:07   Log-Likelihood:                -10866.
No. Observations:                3457   AIC:                         2.174e+04
Df Residuals:                    3451   BIC:                         2.178e+04
Df Model:                           5                                         
Covariance Type:            nonrobust                                         
===============================================================================
                  coef    std err          t      P>|t|      [95.0% Conf. Int.]
-------------------------------------------------------------------------------
Intercept       4.6960      0.550      8.532      0.000         3.617     5.775
W               0.3292      0.382      0.861      0.390        -0.421     1.079
S              -0.7225      0.341     -2.121      0.034        -1.390    -0.055
DW20            1.8791      0.646      2.910      0.004         0.613     3.145
polchange      -2.4816      1.047     -2.371      0.018        -4.534    -0.429
np.log(pop)    -0.0261      0.056     -0.468      0.640        -0.136     0.083
==============================================================================
Omnibus:                      408.738   Durbin-Watson:                   1.512
Prob(Omnibus):                  0.000   Jarque-Bera (JB):             4176.816
Skew:                          -0.006   Prob(JB):                         0.00
Kurtosis:                       8.385   Cond. No.                         99.7
==============================================================================

Warnings:
[1] Standard Errors assume that the covariance matrix of the errors is correctly specified.
\end{verbatim}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df['Klepto'] = (df['TAXGDP']-df['Expenditure']).abs()
df = df[['regyr','ccode','aid_gdp','lrgdpc','pop','year','W','S','Klepto','laglrgdpc']]
\end{minted}
